Data Archiving Attitudes

### 2015-06-08 analysis.Rmd
Analysis update following the parsedate workaround.

library(parsedate)
library(plyr)
library(dplyr)
library(zoo)
library(ggplot2)
library(assertthat)

@@

# determine time since JDAP introduction in the journal where the article was published
d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")

d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
# d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")

@@

d$label_PolicyAdoptedAtPublication <- gsub(" ", "\n", d$PolicyAdoptedAtPublication)

@@

responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom

tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)

p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

>>>>

library(plyr)
library(dplyr)
library(zoo)
library(ggplot2)
library(assertthat)
source("./src/aux_functions.R")

@@

d$PolicyStartDate <- parse_date(d$policy_start)

# determine time since JDAP introduction in the journal where the article was published
d$DaysPolicyToPublication <- difftime(d$PublicationDate, d$PolicyStartDate, units="days")
d$DaysPolicyToResponse <- difftime(d$ResponseDate, d$PolicyStartDate, units="days")

levels_TimeClass <- c("No JDAP","Before JDAP","After JDAP") 
levels_TimeClassByYear <- c("No\nJDAP","Before\nJDAP","1st Year\nAfter\nJDAP", "1+ Year\nAfter\nJDAP") 
d$PolicyAdoptedAtPublication <- ifelse(is.na(d$DaysPolicyToPublication), levels_TimeClass[1], ifelse(d$DaysPolicyToPublication<0, levels_TimeClass[2], levels_TimeClass[3]))
d$PolicyAdoptedAtResponse <- ifelse(is.na(d$DaysPolicyToResponse), levels_TimeClass[1], ifelse(d$DaysPolicyToResponse<0, levels_TimeClass[2], levels_TimeClass[3]))

d$PolicyAdoptedAtPublicationByYears <- ifelse(is.na(d$DaysPolicyToPublication), levels_TimeClassByYear[1], ifelse(d$DaysPolicyToPublication<0, levels_TimeClassByYear[2], ifelse(d$DaysPolicyToPublication<365, levels_TimeClassByYear[3], levels_TimeClassByYear[4] )))
d$PolicyAdoptedAtResponseByYears <- ifelse(is.na(d$DaysPolicyToResponse), levels_TimeClassByYear[1], ifelse(d$DaysPolicyToResponse<0, levels_TimeClassByYear[2], ifelse(d$DaysPolicyToResponse<365, levels_TimeClassByYear[3], levels_TimeClassByYear[4] )))

@@

# unique(d$PolicyAdoptedAtPublication)
# d$label_PolicyAdoptedAtPublication <- ordered(d$PolicyAdoptedAtPublication, levels=c("No\nJDAP", "Before\nJDAP", "After\nJDAP"))
d$label_PolicyAdoptedAtPublication <- ordered(gsub(" ","\n",d$PolicyAdoptedAtPublication), levels=gsub(" ","\n",levels_TimeClass))

# Note: These are very surprising responses
# d_unexpected_responses <- subset(d, label_PolicyAdoptedAtPublication==levels_TimeClassByYear[4]) %>% subset(Q_9 == "Strongly Agree")
#d_unexpected_responses$Q_9 %>% summary
#summary(as.factor(d_unexpected_responses$Journal))
#d_unexpected_responses %>% head(2)

#head(d_unexpected_responses,3)
#subset(d_unexpected_responses, )

@@

responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
question_labels <- c('Q_1'='"Data sharing is a community norm."\n(Question 1)',
                     'Q_2'='"Data archiving is a community norm."\n(Question 2)',
                     'Q_9'='"I would seek alternative journals\nif JDAP was introduced."\n(Question 9)')
tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
tmp$variable <- as.character(tmp$variable)
tmp$variable <- ordered(nmap(tmp$variable, question_labels), levels=question_labels)
#tmp$variable <- gsub("Q_", "Question ", tmp$variable) # gsub("Q_", "Question ", tmp$variable)

p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
print(p)
